---
title: "assignemnt04 first graph"
output: html_document
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(message = FALSE)
knitr::opts_chunk$set(warning = FALSE)
```



```{r include =  FALSE}
library(tidyverse)
library(ggplot2)
library(readxl)
corruption <- read_excel("corruption.xlsx")
```

## Internet Penetration Rate and Local corruption

This plot explore the negative relationship between provincial internet penetration rate and degree of local corruption in different economic zones of China. As the development of E-government in recent years facilitates citizens to supervise government daily operation, provinces with higher internet penetration rate appear to have fewer corruption cases.

This finding implies that better infrastructures can empower citizens to monitor local governments as news media, reshaping the system of anti-corruption institutions. 

[Data Source](https://data.stats.gov.cn/index.htm)
[Relevant Academic Work](https://www.sciencedirect.com/science/article/abs/pii/S0167624509000110)
 
```{r  echo = TRUE}
corruption <- corruption %>%
mutate(corruption_per = corruption_officials / non_private_employee)
ggplot(data = corruption,
        mapping = aes(x = corruption_per,
                      y = internet)) +
    geom_point(alpha = 0.2 , color= "blue", position = "jitter") +
    geom_smooth(method="lm", color = "red", linetype = 2, se= FALSE) +
  facet_grid(~region) +  
  coord_cartesian(ylim = c(0, 1)) +
  coord_cartesian(xlim = c(0, 10)) +
  labs(title = "Internet Penetration Rate on Corruption Cases per 10,000 Non-private Employees, by Economic Zone",
       caption = "Data Source: National Bureau of Statistics of China",
       x = "Provincial Annual Corruption Cases per 10,000 Non-private employees",
       y = "Provincial Annual Internet Penetration Rate") +
  theme(strip.background = element_blank(),
        legend.title=element_blank())
```