---
title: "second plot"
output: html_document
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(message = FALSE)
knitr::opts_chunk$set(warning = FALSE)
```



```{r include =  FALSE}
library(tidyverse)
library(ggplot2)
library(readxl)
corruption <- read_excel("corruption.xlsx")
```

## Different period of government and Local corruption

This plot explore how degree of corruption in different economic zones varied in different period of Chinese government. The Chinese Communist Party (CCP) uses 5 years as cycle to institute national plans and policies. The plot indicates that in different period of 5 years plan the degree of corruption in East, West and Central have gradual decrease due to the reform of Chinese anti-corruption system. But Northeast appears to be an outlier. 

This finding implies that Chinese government should pay more attention to the anti-corruption issues in Northeast economic zone. 

[Data Source](https://data.stats.gov.cn/index.htm)

```{r  echo = TRUE}
corruption <- corruption %>%
  mutate(
    period = case_when(
      year == 2003 ~ "16th",
      year == 2004 ~ "16th",
      year == 2005 ~ "16th",
      year == 2006 ~ "16th",
      year == 2007 ~ "16th",
      year == 2008 ~ "17th",
      year == 2009 ~ "17th",
      year == 2010 ~ "17th",
      year == 2011 ~ "17th",
      year == 2012 ~ "17th",
      year == 2013 ~ "18th",
      year == 2014 ~ "18th",
      year == 2015 ~ "18th",
      year == 2016 ~ "18th",
      year == 2017 ~ "18th"
    ))
period_level <- c("16th","17th","18th")
corruption$period <- factor(corruption$period, 
                            levels = period_level)
region_level <- c("East", "Northeast", "Central", "West")
corruption$region <- factor(corruption$region, 
                            levels = region_level)
ggplot(data = corruption) +
  geom_boxplot(mapping = aes(x = period,
                             y = corruption_per,
                             fill = region,
                             color = region,
                             outlier.size = 2,
                             outlier.alpha = 0.4),
               width = 0.5,
               alpha = 0.4) +
  scale_fill_manual(values = c("East" = "blue",
                               "Northeast" = "red",
                               "West" = "orange",
                               "Central" = "purple")) +
  scale_color_manual(values = c("East" = "blue",
                               "Northeast" = "red",
                               "West" = "orange",
                               "Central" = "purple")) +
  coord_cartesian(ylim = c(0, 8)) +
  theme(legend.title=element_blank()) +
  labs(title = "Corruption Cases per 10,000 Non-private Employees on CCP National COngresses, by Economic Zone",
       caption = "Data Source: National Bureau of Statistics of China",
       x = "CCP National Congress",
       y = "Provincial Annual Corruption Cases per 10,000 Non-private employees")
```





